---
title: "P8105_hw1_dry2115"
author: "Dayoung Yu"
date: 2018-09-21
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

## Problem 1

A data frame containing four variables (random sample, logic vector, character vector, and factor vector) was created:
```{r prob1_1}
set.seed(2115)

df_uniform = tibble(
  
    uniform_sample = runif(10, min = 0, max = 5),
    
    greater_than_2 = (uniform_sample > 2),
    
    char_vec = c("a","b","c","d","e","f","g","h","i","j"),
    
    factor_vec = factor(c(0,1,1,0,0,1,0,1,1,1), 
                 levels = c(0, 1), 
                 label = c("fruit", "vegetable"))
)

df_uniform


```

The mean of each variable was calculated:

```{r prob1_2, warning = FALSE}
df_means = tibble(
  
    mean_sample = mean(df_uniform$uniform_sample),
    mean_logic = mean(df_uniform$greater_than_2),
    mean_char = mean(df_uniform$char_vec),
    mean_factor = mean(df_uniform$factor_vec)
)

df_means

```

Means were obtained for the uniform sample variable and logic variable because they consisted of valid numeric values. The logic variable is given values of 0 or 1. The mean function yielded "NA" for the character variable and factor variable because means cannot be calculated for character strings or categorical data.


The logic, character, and factor variables were converted to numeric vectors:
```{r prob1_3, results = "hide", warning = FALSE}

  as.numeric(df_uniform$greater_than_2)
  as.numeric(df_uniform$char_vec)
  as.numeric(df_uniform$factor_vec)

```
Results: The logic vector was converted to corresponding numeric values of 0 and 1 while the factor vector was converted to values of 1 and 2. The character vector could not be converted to numeric.

Character variable converted to factor to numeric, and factor variable converted to charater to numeric:
```{r prob1_4, warning = FALSE}

  char_fact = as.factor(df_uniform$char_vec)
  char_fact_num = as.numeric(char_fact)
  char_fact_num
  
  fact_char = as.character(df_uniform$factor_vec)
  fact_char_num = as.numeric(fact_char)
  fact_char_num

```
The character variables were assigned into factors from 1-10, then converted into corresponding numeric values. The factor variables were converted to corresponding character strings of "fruit" or "vegetable", but the resulting character values could not be converted to numeric values.


## Problem 2

A data frame was created containing two normal random samples of size n=1000.
```{r prob2}

df_normal = tibble(
  
    x = rnorm(1000),
    y = rnorm(1000),
  
    positive_sum = (x + y > 0),
    num_coerce = as.numeric(positive_sum),
    factor_coerce = as.factor(positive_sum)
)

df_normal

```



Descriptive statistics were calculated for the random samples x and y:
```{r prob2_descr}

  n_x = length(df_normal$x)
  mean_x = mean(df_normal$x)
  median_x = median(df_normal$x)
  total_true = length(df_normal$positive_sum[df_normal$positive_sum == TRUE])
  prop_true = (total_true / n_x)
  
  
  n_y = length(df_normal$y)
  mean_y = mean(df_normal$y)
  median_y = median(df_normal$y)

```

The random sample x has sample size n = `r n_x`, mean = `r mean_x`, and median = `r median_x`.
The random sample y has sample size n = `r n_y`, mean = `r mean_y`, and median = `r median_y`.
The proportion of cases where x + y > 0 is `r prop_true`.


