---
title: "P8105_hw1_dry2115"
author: "Dayoung Yu"
date: 2018-09-21
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

## Problem 1

A data frame containing four variables is created:
```{r prob1_1}
set.seed(2115)

df_uniform = tibble(
  
    uniform_sample = runif(10, min = 0, max = 5),
    
    greater_than_2 = (uniform_sample > 2),
    
    char_vec = c("a","b","c","d","e","f","g","h","i","j"),
    
    factor_vec = factor(c(0,1,1,0,0,1,0,1,1,1), 
                 levels = c(0, 1), 
                 label = c("fruit", "vegetable"))
)

## print data frame
df_uniform


```

The mean of each variable is calculated:

```{r prob1_2}
df_means = tibble(
  
      mean_sample = mean(df_uniform$uniform_sample),
      mean_logic = mean(df_uniform$greater_than_2),
      mean_char = mean(df_uniform$char_vec),
      mean_factor = mean(df_uniform$factor_vec)
)


## print means

df_means

```

Means were obtained for the uniform sample variable and logic variable because they consisted of valid numeric values. The mean function yielded "NA" for the character variable and factor variable because means cannot be calculated for character strings or categorical data.


## Problem 2


```{r prob_2}


```
